### 2020-01-30 wuhan.tex

We gathered information on estimates of $\mathcal R_0$ and their assumptions about the underlying generation-interval distributions from 6 articles that were uploaded to preprint servers between January 24th, 2020 and January 26th, 2020 (Table 1).
For each study $i$, we analyze explicitly or implicitly reported distributions of the reproductive number $\mathcal R_{0i}$, the mean generation interval $\bar G_i$, and the generation-interval dispersion parameter $\kappa_i$ (equivalent to the squared coefficient of variation for a gamma distribution, which matched the assumptions of all of the studies).
We modeled values reported using gamma distributions or confidence intervals with gamma distributions, and values reported using uniform distributions with uniform distributions \jd{SWP pls check}.
For example, Study 2 estimated $\mathcal R_0 = 2.92$ (95\% CI: 2.28--3.67);
we model this parameter as a gamma distribution with a mean of 2.92 and a shape parameter of 67, which has a 95\% probability of containing a value between 2.28 and 3.67 (see Table 2 for a complete description).
If a study assumed a fixed value for a parameter, we hold that parameters constant as well, using the same assumed value. \jd{I kind of want to drop this sentence.}

\begin{table}[t]
\begin{center}
\footnotesize
\begin{tabular}{l|l|l|l}
 & Basic reproductive number & mean generation time (days) & CV$^2$ generation time \\
\hline
Study 1 & $\mathrm{Gamma}(\alpha=28, \beta=28/2.6)$ & constant & constant \\
\hline
Study 2 & $\mathrm{Gamma}(\alpha=67, \beta=67/2.92)$ & constant & constant \\
\hline
Study 3 & N.A. & $\mathrm{Uniform}(6, 10)$ & constant\\
\hline
Study 4 & $\mathrm{Gamma}(\alpha=1400, \beta=1400/3.8)$ & constant & constant \\
\hline
Study 5 & $\mathrm{Gamma}(\alpha=12, \beta=12/2.2)$ & $\mathrm{Uniform}(7, 14)$ & constant\\
\hline
Study 6 & $\mathrm{Gamma}(\alpha=54, \beta=54/5.47)$ & $\mathrm{Uniform}(7.6, 8.4)$ & constant
\end{tabular}
\end{center}
\caption{
\textbf{Probability distributions $\mathcal R_0$, $\bar G$, and $\kappa$.}
We use these 
The probability distribution for the exponential growth rate $r$ for each study is obtained by drawing random samples from these distributions and taking the inverse of \eref{gamma}.
The gamma distribution is parameterized by shape $\alpha$ and rate $\beta$ parameters.
Constant distributions assume a fixed values according to Table 1.
}
\end{table}

We then constructed a family of parameter sets for each study, and used these in a Bayesian multilevel model to build a distribution of pooled estimates (see Methods).

>>>>

We gathered information on estimates of $\mathcal R_0$ and their assumptions about the underlying generation-interval distributions from 6 articles that were uploaded to preprint servers between January 24th, 2020 and January 26th, 2020 (Table 1).
For each study $i$, we analyze explicitly or implicitly reported distributions of the reproductive number $\mathcal R_{0i}$, the mean generation interval $\bar G_i$, and the generation-interval dispersion parameter $\kappa_i$ (equivalent to the squared coefficient of variation for a gamma distribution, which matched the assumptions of all of the studies).
We modeled values reported using confidence intervals with gamma distributions, and values reported using ranges with uniform distributions.
For example, Study 2 estimated $\mathcal R_0 = 2.92$ (95\% CI: 2.28--3.67);
we model this parameter as a gamma distribution with a mean of 2.92 and a shape parameter of 67, which has a 95\% probability of containing a value between 2.28 and 3.67 (see Table 2 for a complete description).
We then constructed a family of parameter sets for each study, and used these in a Bayesian multilevel model to build a distribution of pooled estimates (see Methods).

\begin{table}[t]
\begin{center}
\footnotesize
\begin{tabular}{l|l|l|l}
 & Basic reproductive number & mean generation time (days) & CV$^2$ generation time \\
\hline
Study 1 & $\mathrm{Gamma}(\alpha=28, \beta=28/2.6)$ & constant & constant \\
\hline
Study 2 & $\mathrm{Gamma}(\alpha=67, \beta=67/2.92)$ & constant & constant \\
\hline
Study 3 & N.A.$^\ast$ & $\mathrm{Uniform}(6, 10)$ & constant\\
\hline
Study 4 & $\mathrm{Gamma}(\alpha=1400, \beta=1400/3.8)$ & constant & constant \\
\hline
Study 5 & $\mathrm{Gamma}(\alpha=12, \beta=12/2.2)$ & $\mathrm{Uniform}(7, 14)$ & constant\\
\hline
Study 6 & $\mathrm{Gamma}(\alpha=54, \beta=54/5.47)$ & $\mathrm{Uniform}(7.6, 8.4)$ & constant
\end{tabular}
\end{center}
\caption{
\textbf{Probability distributions $\mathcal R_0$, $\bar G$, and $\kappa$.}
We use these 
The probability distribution for the exponential growth rate $r$ for each study is obtained by drawing random samples from these distributions and taking the inverse of \eref{gamma}.
The gamma distribution is parameterized by shape $\alpha$ and rate $\beta$ parameters.
Constant distributions assume a fixed values according to Table 1.
$^\ast$Study 3 effectively fits an exponential curve to the cumulative number of confirmed cases. \emph{All} uncertainty in their $\mathcal R_0$ estimate can be explained by the uncertainty range they consider for $\bar G$. Instead of modeling $\mathcal R_0$ with a probability distribution and recalculating $r$, we simply fix $r=0.114\,\mathrm{days}^{-1}$.
}
\end{table}
